resistanceModelNotesAndy

### 2016-02-11 paper1_results_figs.Rmd
add PRCC for difference

# Figures for paper 1 
# version 2 - in progress

@@

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) mixture switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure has the greatest effect on time-to-resistance, but as it has a similar effect across all strategies it has little influence on which strategy is preferable.
1. Effectiveness of the insecticides is the one input that has a notably different effect on the strategies of a) sequential and b) mixture switching to sole use. Below an effectiveness of ~0.55 to 0.6 sequential takes longer, and above this 'mixture switching to sole use' takes longer.

@@

# Difference between time-to-resistance for sequential and mixture2

#names_results <- c("time_to_resistance0.5","time_to_resistance0.25","time_to_resistance0.1")
# names_results <- c("mix2_minus_seq0.25")
#   
# ggSubset <- df_diff #[ !ggInsOuts$strategy %in% c("insecticide 2"), ]  
#   
# for(i in names_results)
# {
#   #x11()
#   
#   print( ggplot(ggSubset, aes_string(y=i)) + 
#       #ylim(0,450) +
#       #coord_cartesian( ylim=c(0, 350)) +
#       geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 )
# 
#   ) #end print
# }

@@

## How difference in time-to-resistance for sequential and mixture3 is effected by input values

@@

    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="gen_cP0.25seq")) + #, colour="strategy")) + 
            #points not wanted if 10000
             geom_point(shape=3, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1) +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i))
  }

>>>>

# Figures for paper 1 
# version 3 - in progress

@@

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) mixture switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure and effectiveness seem to be the most important inputs.
1. Exposure has the greatest effect on time-to-resistance.
1. Effectiveness of the insecticides is the one input that has a notably different effect on the strategies of a) sequential and b) mixture switching to sole use. Below an effectiveness of ~0.55 to 0.6 sequential takes longer, and above this 'mixture switching to sole use' takes longer.

@@

@@

## How difference in time-to-resistance between sequential and mixture2 is effected by input values

@@

    print( ggplot(ggSubset, aes_string(x=i, y=y)) + #, colour="strategy")) + 
            #points not wanted if 10000
             geom_point(shape=1, colour="darkblue", alpha=0.2, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1, colour="red") +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i) +
             geom_hline(yintercept = 0, colour="white")
           )
  }

# PRCC difference in time-to-resistance between sequential and mixture2
```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=3.5}

    x <- df_diff[,1:num_inputs]
    y <- df_diff["mix2_minus_seq0.25"]

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             ggtitle(paste("PRCC difference between sequential and mixture2")) +
             xlab(NULL)
          )
